FDT\thanks{Supported by organization x.}

### 2018-11-20 IPCO format/computational.tex
computational experminets

\section{Computational experiments with FDT}\label{experiment}
We implement FDT to two covering problem. First, the tree argumentation problem (TAP) where given a tree $T=(V,E)$, and a set of link $L$ between the vertices in $V$ and costs $c\in \bbbr^{L}_{\geq 0}$ we with to find minimum cost subset $L'$ of $L$ such that $T+L'$ is 2-edge-connected. For $\ell\in L$, let $P_\ell$ be the set of edges in the unique path between the endpoints of $\ell$ in $T$. For TAP, $S(\mbox{TAP})=\{x\in \bbbz^{L}_{\geq 0}: \sum_{\ell: e\in P_\ell}x_\ell \geq 1, \mbox{ for $e\in E$}\}$. Relaxing the integrality constraint we get $P(\mbox{TAP})$. It is been shown that $\frac{3}{2}\leq g({\mbox{TAP}})\leq 2$ \cite{fj,32gap}. We applied the binary FDT algorithm on a set of 264 fractional extreme points of $P(\mbox{TAP})$. The result are summarized in Figure \ref{plotTAP}.

Next we implemented the FDT for 2EC on a 900 fractional extreme points of $\EC(G)$. These points are obtained by considering all fundamental vertices with $12$ vertices (See \cite{CV} for the definition of fundamental vertices). The results are summarized in Figure \ref{plot2EC}. We also, implemented polyhedral version of Christofides' algorithm \cite{Wolsey1980} and compared its performance on fundamental extreme points with 10 vertices. The result are in Figure \ref{}.

>>>>

\section{Computational experiments with FDT}\label{experiment}
We implement FDT to two covering problem. First, the tree argumentation problem (TAP) where given a tree $T=(V,E)$, and a set of link $L$ between the vertices in $V$ and costs $c\in \bbbr^{L}_{\geq 0}$ we with to find minimum cost subset $L'$ of $L$ such that $T+L'$ is 2-edge-connected. For $\ell\in L$, let $P_\ell$ be the set of edges in the unique path between the endpoints of $\ell$ in $T$. For TAP, $S(\mbox{TAP})=\{x\in \bbbz^{L}_{\geq 0}: \sum_{\ell: e\in P_\ell}x_\ell \geq 1, \mbox{ for $e\in E$}\}$. Relaxing the integrality constraint we get $P(\mbox{TAP})$. It is been shown that $\frac{3}{2}\leq g({\mbox{TAP}})\leq 2$ \cite{fj,32gap}. We applied the binary FDT algorithm on a set of 264 fractional extreme points of $P(\mbox{TAP})$. The result are summarized in Table \ref{tableTAP}. 
\begin{table}[h]
	\centering
	  \begin{tabular}{c c c c c}
	  \toprule
	  	& $C\in [1.1,1.2]\;$ & $\;C\in (1.2,1.3]\;$ &
               $\;C\in (1.3,1.4]$ &\; $C\in (1.4,1.5]\;$ \\ \midrule
	  	TAP & $36$ & $66$ & $170$ & $10$\\  \bottomrule \\
	  \end{tabular}\caption{FDT impletemented applied to 264 randomly generated TAP instances with fractional extreme points: 138 of the 264 have $74$ variables, so the theoretical guarantee of Theorem \ref{binaryFDT} is at least $(1.5)^{74}$. For the rest, the number of variables in $250$.}
	  \label{tableTAP}
\end{table}
Next we implemented the FDT for 2EC on a 963 fractional extreme points of $\EC(G)$. These points are obtained by considering all fundamental vertices with $10$ and $12$ vertices (See \cite{CV} for the definition of fundamental vertices). The results are summarized in Table \ref{table2EC}. 
\begin{table}[h]
	\centering
	  \begin{tabular}{c c c c c}
	  	\toprule
	  	& $C\in [1.08,1.11]\;$ & $\;C\in (1.11,1.14]\;$ &
               $\;C\in (1.14,1.17]$ &\; $C\in (1.17,1.2]\;$ \\ \midrule
	  	2EC & $79$ & $201$ & $605$ & $78$ \\ \bottomrule\\
	  \end{tabular}\caption{FDT for $\EC$ implemented applied to all fundamental extreme points with 10 and 12 vertices. The number of variables for a fundamental extreme point with $k$ vertices is $\frac{3k}{2}$ and the lower bound on $g_\EC$ is $\frac{6}{5}$.}
	  \label{table2EC}
\end{table}
We also implemented polyhedral version of Christofides' algorithm \cite{Wolsey1980} and compared its performance on fundamental extreme points with 10 vertices. The result are in Figure \ref{fdtvschris}.
\begin{figure*}%
\centering
\includegraphics[width=8cm]{"fdt vs christofides".png}}
\caption{Christofides' algorithm vs FDT on all fundamental extreme points with 10 vertices.}
\label{fdtvschris}
\end{figure*}

### 2018-11-20 IPCO format/introduction.tex
computational experminets

In attempt to extend our results into $\{0,1,2\}$-MILPs we give an FDT algorithm for the 2-edge-connected multigraph problem. In this problem we want to find the minimum weight 2-edge-connected subgraph (which can multiple copies of each edge) in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$. For this problem the natural linear programming relaxation is
\begin{equation}\label{2ECpol}
\EC(G)= \{x\in \bbbr_{\geq 0}^{E}\;:\; x(\delta(S))\geq 2 \text{ for $\emptyset \subset S\subset V$})\}.\end{equation}
We prove the following theorem.

@@

Finally we give a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems. For this purpose assume $P= \{x\in \bbbr^n_{\geq 0}: Ax\geq b\textbf{1}, x \leq b\textbf{1}\}$, $S= P\cap \bbbz^n$, and $g= \max_{c\geq 0} \frac{\min_{x\in S}cx}{\min_{x\in P}cx}$. Examples of such problems include the 2-edge-connected multigraph problem, the tree augmentation problem, and many others.

@@

This means in order to prove an upper bound on the integrality gap of a covering problem, we need to show there is a convex combination of integer feasible points that is ``cheap'' on all tight cuts. Notice that Theorem \ref{CV} requires the certificate convex combination to be ``cheap" on every single variable.

\subsection{Notations}
For vectors $x,y\in \bbbr_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$. For $m\times n$ matrix $A$, let $A_j$ be the $j$-th row of $A$ and $A^j$ be the $j$-th column of $A$. Let $\textbf{1}$ be the vector of all ones of a suitable dimension. For a set $S$ of vectors in $\bbbr_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.

>>>>

In an attempt to extend our results into $\{0,1,2\}$-MILPs we give an FDT algorithm for the 2-edge-connected multigraph problem. In this problem we want to find the minimum weight 2-edge-connected subgraph (which can multiple copies of each edge) in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$. For this problem the natural linear programming relaxation is
\begin{equation}\label{2ECpol}
\EC(G)= \{x\in \bbbr_{\geq 0}^{E}\;:\; x(\delta(S))\geq 2 \text{ for $\emptyset \subset S\subset V$})\}.\end{equation}
We prove the following theorem.

@@

\iffalse{
Finally we give a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems. For this purpose assume $P= \{x\in \bbbr^n_{\geq 0}: Ax\geq b\textbf{1}, x \leq b\textbf{1}\}$, $S= P\cap \bbbz^n$, and $g= \max_{c\geq 0} \frac{\min_{x\in S}cx}{\min_{x\in P}cx}$. Examples of such problems include the 2-edge-connected multigraph problem, the tree augmentation problem, and many others.

@@

This means in order to prove an upper bound on the integrality gap of a covering problem, we need to show there is a convex combination of integer feasible points that is ``cheap'' on all tight cuts. Notice that Theorem \ref{CV} requires the certificate convex combination to be ``cheap" on every single variable.
\subsection{Notations}
For vectors $x,y\in \bbbr_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$. For $m\times n$ matrix $A$, let $A_j$ be the $j$-th row of $A$ and $A^j$ be the $j$-th column of $A$. Let $\textbf{1}$ be the vector of all ones of a suitable dimension. For a set $S$ of vectors in $\bbbr_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.
}\fi
